Probabilistic inference in dynamical systems

### 2024-07-28 nbs/concepts/inferenceindynamicalsystems/index.qmd
fix(nbs): escape apostrophes
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

We'll solve the dimensionless system analytically, focusing on what can be 
understood about the system's dynamics.
Given specific initial conditions $u^{\ast}(0) = u^{\ast}_0$ and 
$s^{\ast}(0) = s^{\ast}_0$, which we restore to arbitrary $t^{\ast}_0$ 
at the end of the derivation, the first equation

@@

The analytical solutions to the dimensionless system reveal how the pre-mRNA 
and mRNA concentrations evolve over time towards their steady states. The 
exponential terms highlight the system's inherent timescales: $u^{\ast}$ relaxes 
to its steady state independently, while $s^{\ast}$’s dynamics are coupled to 
both $u^{\ast}$ and its own degradation rate. While this system is extremely
simplified relative to well-known biology, as a stylized model it still
indicates the interplay among transcription, splicing, and degradation rates.

>>>>

We'll solve the dimensionless system analytically, focusing on what can be 
understood about the system\'s dynamics.
Given specific initial conditions $u^{\ast}(0) = u^{\ast}_0$ and 
$s^{\ast}(0) = s^{\ast}_0$, which we restore to arbitrary $t^{\ast}_0$ 
at the end of the derivation, the first equation

@@

The analytical solutions to the dimensionless system reveal how the pre-mRNA 
and mRNA concentrations evolve over time towards their steady states. The 
exponential terms highlight the system\'s inherent timescales: $u^{\ast}$ relaxes 
to its steady state independently, while $s^{\ast}$’s dynamics are coupled to 
both $u^{\ast}$ and its own degradation rate. While this system is extremely
simplified relative to well-known biology, as a stylized model it still
indicates the interplay among transcription, splicing, and degradation rates.
